
\begin{thebibliography}{}

    \bibitem{Quantum tunneling}
    \textit{Quantum tunneling in zener diodes},
    \url{https://physics.stackexchange.com/questions/466615/quantum-tunneling-in-zener-diodes}, (2019)

    \bibitem{A survey of known results and research areas for}
    J. Bell and B. Stevens, “A survey of known results and research areas for,” \textit{Discrete Mathematics}, vol. 309, no. 1, pp. 1–31, 2009.
    
      \bibitem{The computer as a physical system}
    Benioff, P., 1980. The computer as a physical system: A microscopic quantum mechanical Hamiltonian model of computers as represented by Turing machines. \textit{Journal of statistical physics}, 22, pp.563-591.

    \bibitem{Simulating physics with computers}
    Feynman, R.P., 2018. Simulating physics with computers. In \textit{Feynman and computation} (pp. 133-153). CRC Press.

    \bibitem{Quantum computational networks}

    Deutsch, D.E., 1989. Quantum computational networks. \textit{Proceedings of the royal society of London. A. mathematical and physical sciences}, 425(1868), pp.73-90.

    \bibitem{A Fast Quantum Mechanical Algorithm for Database Search}
    Grover, L.K., 1996, July. A fast quantum mechanical algorithm for database search. In \textit{Proceedings of the twenty-eighth annual ACM symposium on Theory of computing} (pp. 212-219).

    \bibitem{An approximate Fourier transform useful in quantum factoring}
    Coppersmith, D., 2002. An approximate Fourier transform useful in quantum factoring. \textit{arXiv preprint quant-ph/0201067.}

    \bibitem{Adiabatic quantum computation}
    Albash, T. and Lidar, D.A., 2018. Adiabatic quantum computation. \textit{Reviews of Modern Physics, 90(1)}, p.015002.

    \bibitem{Evidence for quantum annealing with more than one hundred qubits}
    Sergio Boixo, Troels F Rønnow, Sergei V Isakov, Zhihui Wang, David Wecker, Daniel A Lidar, John M Martinis, and Matthias Troyer. Evidence for quantum annealing with more than one hundred qubits. \textit{Nature Physics}, 10(3):218, 2014. DOI: 10.1038/nphys2900.

    \bibitem{A quantum annealin architecture with all-to-all connectivity from local interactions}
    Wolfgang Lechner, Philipp Hauke, and Peter Zoller. A quantum annealin architecture with all-to-all connectivity from local interactions. \textit{Science Advances}, 1(9), 2015. DOI: 10.1126/sciadv.1500838.

    \bibitem{Minor-embedding in adiabatic quantum computation: I. the parameter setting problem}
    Vicky Choi. Minor-embedding in adiabatic quantum computation: I. the parameter setting problem. \textit{Quantum Information Processing}, 7(5):193–209, 2008. DOI: 10.1007/s11128-008-0082-9.
  
    \bibitem{Ising formulations}
    Lucas, A., 2014. 
    \textit{Ising formulations of many NP problems. Frontiers in physics}, 2, p.74887.
  
    \bibitem{Proposal of eight queens problem}
    F. W. M. Bezzel, “Proposal of eight queens problem,” \textit{Berliner Schachzeitung}, vol. 3, p. 363, 1848.
	
    \bibitem{Topologies}
    \textit{D-Wave QPU Architecture: Topologies},
    \url{https://docs.dwavesys.com/docs/latest/c_gs_4.html}
    
    \bibitem{dynamic programming solution}
    Rivin, I. and Zabih, R., 1992. "A dynamic programming solution to the n-queens problem". 
    \textit{Information Processing Letters}, 41(5), pp.253-256.
 
    \bibitem{N Queens Dwave}
    \textit{N Queens}, \url{https://github.com/dwave-examples/n-queens} (2023).
 
    \bibitem{Problem Formulation Guide}
    \textit{Problem Formulation Guide}, \url{https://www.dwavesys.com/media/bu0lh5ee/problem-formulation-guide-2022-01-10.pdf}, (2022)
   
    \bibitem{Performance Update}
    Catherine McGeoch and Pau Farré, 
    \textit{The Advantage System: Performance Update}, (2021).
   
 
\end{thebibliography}